figures_manuscript

### 2024-10-17 pub_figures/manuscript-figures.Rmd
fix volcano ratio

# Fig 3: Volcanos
```{r volcanos, fig.height=8 }

@@

ggsave(paste(fig,"_",colData(dds)$experiment[1],"_Volcanos.pdf",sep=""), plot = volcanos_all,
width = 8,
height = 6)

@@

## Fig 4b: groups
```{r groups}

res_
DEGs_comb <- bind_cols(DEGs[[1]],DEGs[[2]],DEGs[[3]])

>>>>

# Fig 3: Volcanos
```{r volcanos, fig.height=6, fig.width=10}

@@

ggsave(paste(fig,"_",colData(dds)$experiment[1],"_Volcanos.pdf",sep=""), plot = volcanos_all,
width = 10,
height = 6)

@@

## Fig 4b: Groups
```{r groups, eval=FALSE}

res_core <- list(dark = res_list$pcry$pcry_D.vs.WT_D,
             blue = res_list$pcry$pcry_BL.vs.WT_BL,
             red =res_list$pcry$pcry_R.vs.WT_R) %>% lapply(data.frame)

DEGs_comb <- bind_cols(res_core[[1]][],res_core[[2]],res_core[[3]])
